Coverletter

### 2021-02-16 paper/natastron/Publication/coverletter.tex
done coverletter

\documentclass[11pt, a4paper, sans, colorlinks, linkcolor=True]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage{ragged2e}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
%\addtolength{\topmargin}{-.875in}
\pagenumbering{gobble}
\usepackage{setspace}

@@

We hope this letter finds you well. We have completed our response to the reviewer, which is attached below this cover letter (and uploaded separately with resubmission). Major changes to the text are coloured red. Please note that this includes a change to the title. No changes have been made to the Supplementary Information.

At the moment, our main results table is still in Extended Data, as we don't think it is necessary to include it in the main text. Ideally we would publish this table digitally along with the article (as well as host it on Vizier). If you have any input on whether this table should be (partially) included in the main text, or other thoughts on how to best present it in the Nature Astronomy format, we would be grateful.

The word count breakdown is as follows:
\begin{itemize}
	\item Abstract: 196
	\item Introduction: 499
	\item Main body (incl. Introduction): 2886
	\item Methods: 5507
	\item Supplementary Information: 2544
\end{itemize}

And the number of figures, tables and references are as follows:
\begin{itemize}
	\item Main body: 4 figures (1.2 MB), 51 references
	\item Methods: 0 figures, 57 references
	\item Supplementary Information: 1 figure (298 KB), 25 references
	\item Extended Data: 5 Figures (1.1 MB), 1 Table (4 pages, 29 KB), 10 references
\end{itemize}

The references in the \textbf{Extended Data} are numbered following the references listed under Methods.
\vspace{0.5cm}

>>>>

\documentclass[11pt, a4paper, sans, colorlinks, linkcolor=True]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage{ragged2e}
\usepackage[utf8]{inputenc}
%\usepackage{enumitem}
\usepackage[left=1in, right=1in, bottom=0.5in, top=0.5in]{geometry}
%\addtolength{\topmargin}{-.875in}
\pagenumbering{gobble}
\usepackage{setspace}

@@

We have made the requested changes, including those discussed over email, to the best of my ability. Please don't hesitate to get in touch if anything is missing!

For the purposes of advertising this work on Twitter, my handle is @asteronomer.

Those of other authors involved (that have Twitter) are:
\begin{itemize}
	\item Guy R. Davies: @CitationWarrior\\
	\item Mikkel N. Lund: @miklnl41\\
	\item Saniya Khan: @rilasani\\
	\item Victor See: @AstroVictorSee\\
	\item Jamie Tayar: @StellarTayar\\
\end{itemize}

I'll leave it up to you whether you want to them. The institutional handles are, in order of appearance on the manuscript:

\begin{itemize}
	\item @ESAscience\\
	\item @unibirmingham\\
	\item @sacscience\\
	\item @UHIfA\\
	\item @CEAIrfu\\
	\item @UniofExeter\\
\end{itemize}
